The packaging requirements for the UR20 robot and custom-designed gripper will include pre-installed control software. Additionally, the custom gripper will be fully assembled and contained in a single package. The requirements focus on making the product easily deployable and ready for use in palletizing operations.
\subsection{Pre-Installed Software}
\subsubsection{Description}
The control software for operating the UR20 robot will be pre-installed on the the system before delivery to the customer. The robot can immmediately perform palletizing application upon arrival without complex installation procedures. 
\subsubsection{Source}
CSE Senior Design Project Specifications
\subsubsection{Constraints}
The software must be compatible with the UR20 system and ensure reliable functionality. Limited modifications will be needed by customer post-installation.
\subsubsection{Standards}
ISO/IEC/IEEE 12207:2017 Systems and software engineering — Software life cycle processes - proper installation and support for future updates
\subsubsection{Priority}
High
\subsection{Gripper Assembly and Packaging}
\subsubsection{Description}
The gripper mechanism, including vacuum suction cups, will be delivered pre-assembled and tested for immediate use with the UR20 robot. All components will be securely packaged to avoid damage during transportation. 
\subsubsection{Source}
CSE Senior Design Project Specifications
\subsubsection{Constraints}
The packaging must ensure the safe transport of the assembled gripper, sourcing of packaging material will be the responsibility of the engineering team.
\subsubsection{Standards}
ISO 3676:2012 Packaging — Complete, filled transport packages and unit loads — Unit load dimensions ensuring products arrive safely from their origin to their destination.
\subsubsection{Priority}
High